---
title: "Introduction"
format: html
---

## Opening R documentation

You can access R help files in several ways. If you know the name of the 
function or package you are looking for information about, you can use the `?`
operator with the name of the function to open the R help file. This will only 
open documentation for functions and packages you currently have **loaded** 
into R.

```{r}

?summary

```

If you are using RStudio this will bring up documentation for that function in
help window. If you use the GUI, it will open a separate help window. If you are
running R in bash or zsh, R will open the help file in your default text editor.

If you are unsure of the function name, you can use the `??` operator to search
all of your R documentation for a term or set of terms. For multiple search 
terms, enclose them in tick marks.

```{r}

??`linear model`

```


This will search documentation for all packages you have **installed**. It will
then provide a list links to documentation pages you can browse and use to find
the function that works best for your use case. Functions are labeled using the 
schema [PACKAGE NAME]::[FUNCTION NAME] so you can tell which package to load to 
access function you are interested in.

If you want to search documentation for packages that you haven't installed yet,
you have a couple of options. If you are only looking for packages that are
available through [CRAN][cran] or [bioconductor][bioC], you can use
[rdocumentation.org][rdoc]. CRAN itself contains a lot of documentation for each
package on the package's page (ex. [dplyr][dply]), but the information isn't 
searchable from the website and you have to know what package you want 
information on. If you also want to be able to search packages hosted on R-forge
and Github in addition to CRAN and bioconductor, you can use [rdrr.io][rdrr]. 

[dply]: https://cran.r-project.org/web/packages/dplyr/index.html
[cran]: https://cran.r-project.org/
[bioC]: https://www.bioconductor.org/packages/release/BiocViews.html#___Software
[rdoc]: https://www.rdocumentation.org/
[rdrr]: https://rdrr.io/
